---
title: Report of the 1st wave of the survey on Pets, COVID-19 and isolation conducted on from 13th April-17th April)
  
#bibliography: referencescafo.bib 
#csl: elsevier-vancouver.csl
output:
  html_document: default
  pdf_document: default
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
 \usepackage{xcolor}
---
<div style="margin-bottom:100px;">
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# \textcolor{red}{Project Summary: Pet outcomes}

This should be added

# Purpose of the Project


# Brief Summary




# Basic Description of the Participants
```{r figur1,echo = FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(knitr)
library(xtable)
#importing the data and arranging properly
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
numResponces<-nrow(turk)
#frequency grouped by outcomes and year
###Table 1
pets <- turk %>% group_by(PetOwner)
## of reported pets
numPET <-  turk %>%
            dplyr::filter(PetOwner == 1) %>%
            tally() %>%
            .[,"n"]
numDOG <-  turk %>%
            dplyr::filter(PetOwner == 1, PetTypes_1 != 0) %>%
            tally() %>%
            .[,"n"]
numCAT <-  turk %>%
            dplyr::filter(PetOwner == 1, PetTypes_2 != 0) %>%
            tally() %>%
            .[,"n"]
numHORSE <-  turk %>%
            dplyr::filter(PetOwner == 1, PetTypes_3 != 0) %>%
            tally() %>%
            .[,"n"]
numBIRD <-  turk %>%
            dplyr::filter(PetOwner == 1, PetTypes_4 != 0) %>%
            tally() %>%
            .[,"n"]
numREPTILE <-  turk %>%
            dplyr::filter(PetOwner == 1, PetTypes_5 != 0) %>%
            tally() %>%
            .[,"n"]
numSM <-  turk %>%
            dplyr::filter(PetOwner == 1, PetTypes_6 != 0) %>%
            tally() %>%
            .[,"n"]
numFISH <-  turk %>%
            dplyr::filter(PetOwner == 1, PetTypes_7 != 0) %>%
            tally() %>%
            .[,"n"]
numOTHER <-  turk %>%
            dplyr::filter(PetOwner == 1, PetTypes_8 != 0) %>%
            tally() %>%
            .[,"n"]
numDOGCAT <-  turk %>%
            dplyr::filter(PetOwner == 1, PetTypes_1 != 0, PetTypes_2 !=0) %>%
            tally() %>%
            .[,"n"]
propPET<-round((numPET/numResponces)*100,1)
propDOG<-round((numDOG/numPET)*100,1)
propCAT<-round((numCAT/numPET)*100,1)
propHORSE<-round((numHORSE/numPET)*100,1)
propFISH<-round((numFISH/numPET)*100,1)
propREPTILE<-round((numREPTILE/numPET)*100,1)
propOTHER<-round((numOTHER/numPET)*100,1)
propSM<-round((numSM/numPET)*100,1)
propDOGCAT<-round((numDOGCAT/numPET)*100,1)
```

The survey was conducted in April 2020, and `r numResponces` responces were obtained. Of these `r numResponces` respondents, `r numPET` reporting owning pets (`r propPET`%).  Of the pet owners,  `r numDOG` (`r propDOG`%) reported owning dogs, `r numCAT`(`r propCAT`%) reported owning cats, `r numHORSE`(`r propHORSE`%) reported owning horses, `r numREPTILE` (`r propREPTILE`%) reporting owning reptiles, `r numSM` (`r propSM`%) reporting owning small mammals, `r numFISH` (`r propFISH`%) reporting owning fish and `r numOTHER`(`r propOTHER`%) reported owning other animals. `r numDOGCAT` reported owning both cats and dogs.  

```{r tables, results="asis"}
library(xtable)
library(broom)
X <- summary(turk$age)
X <- tidy(X)
kable(X,
      align = "rrrrr",
      caption = "Summary characteritics for age.",
      digits = 0)
mean_age<-round(X[4],0)
med_age<-round(X[3],0)
#col.names = c("min", "Quart1", "med", "mean", "Qurt 3", "max"),

```

The mean age of particiants was `r mean_age` and the median was `r med_age`.

## Kessler responces for the participants

### During the past two weeks, how often did you feel tired for no good reason?

```{r kessler1, echo=F, warning=F} 
library(dplyr)

library(forcats)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Kessler1 <-
  factor(
    turk$Kessler1,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#turk$PetOwner <- factor(turk$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes")) %>% fct_explicit_na("Missing")
#$turk$Kessler1 <- factor(turk$Kessler1, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time")) %>% fct_explicit_na("Missing")
Kessler1 <-
  turk %>% group_by(PetOwner, Kessler1) %>% summarise(Frequency = length(Kessler1))
t1 <- table(turk$PetOwner, turk$Kessler1)
kable(t1, caption = "Contingency table for Kessler 1 responces and Pet Ownership")
ggplot(Kessler1, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler1
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 1 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel tired for no good reason?")

ggplot(Kessler1, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler1
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 1 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel tired for no good reason?")
#making tables


ggplot(Kessler1, aes(
  fill = (Kessler1),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 1 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel tired for no good reason?")
#making tables


Kessler1.fit = glm(PetOwner ~ Kessler1, family = binomial, data = turk)
kable(summary(Kessler1.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
###  "During the past two weeks, how often did you feel nervous? 
```{r kessler2, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Kessler2 <-
  factor(
    turk$Kessler2,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )
#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")

t2 <- table(turk$PetOwner, turk$Kessler2)
kable(t2, caption = "Contingency Table for Kessler 2 responces and Pet Ownership")

Kessler2 <-
  turk %>% group_by(PetOwner, Kessler2) %>% summarise(Frequency = length(Kessler2))

ggplot(Kessler2, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler2
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 2 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often did you feel nervous?")

ggplot(Kessler2, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler2
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 2 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often did you feel nervous?")
#making tables

ggplot(Kessler2, aes(
  fill = (Kessler2),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 2 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel nervous?")

Kessler2.fit = glm(PetOwner ~ Kessler2, family = binomial, data = turk)
kable(summary(Kessler2.fit)$coef, digits = 2)
```

<div style="margin-bottom:100px;">
## "During the past two weeks, how often did you feel so nervous that nothing could calm you down??"
```{r kessler3, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Kessler3 <-
  factor(
    turk$Kessler3,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
t3 <- table(turk$PetOwner, turk$Kessler3)
kable(t3, caption = "Contingency Table for Kessler 3 responces and Pet Ownership")

Kessler3 <-
  turk %>% group_by(PetOwner, Kessler3) %>% summarise(Frequency = length(Kessler3))
ggplot(Kessler3, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler3
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 3 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often \ did you feel so nervous that nothing could calm you down??")


ggplot(Kessler3, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler3
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 3 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often \ did you feel so nervous that nothing could calm you down??")



ggplot(Kessler3, aes(
  fill = (Kessler3),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 3 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often \ did you feel so nervous that nothing could calm you down??")


Kessler3.fit = glm(PetOwner ~ Kessler3, family = binomial, data = turk)
kable(summary(Kessler3.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
## "During the past two weeks, how often did you feel hopeless?"
```{r kessler4, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Kessler4 <-
  factor(
    turk$Kessler4,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
t4 <- table(turk$PetOwner, turk$Kessler4)
kable(t4, caption = "Contingency Table for Kessler 4 responces and Pet Ownership")

Kessler4 <-
  turk %>% group_by(PetOwner, Kessler4) %>% summarise(Frequency = length(Kessler4))
ggplot(Kessler4, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler4
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 4 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often did you feel hopeless?")

ggplot(Kessler4, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler4
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 4 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often did you feel hopeless?")

ggplot(Kessler4, aes(
  fill = (Kessler4),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 4 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often did you feel hopeless?")

Kessler4.fit = glm(PetOwner ~ Kessler4, family = binomial, data = turk)
kable(summary(Kessler4.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
## *"During the past two weeks, how often did you feel restless or fidgety?"*
```{r kessler5, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Kessler5 <-
  factor(
    turk$Kessler5,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
t5 <- table(turk$PetOwner, turk$Kessler5)
kable(t5, caption = "Contingency Table for Kessler 5 responces and Pet Ownership")

Kessler5 <-
  turk %>% group_by(PetOwner, Kessler5) %>% summarise(Frequency = length(Kessler5))
ggplot(Kessler5, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler5
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 5 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel restless or fidgety")

ggplot(Kessler5, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler5
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 5 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel restless or fidgety")

ggplot(Kessler5, aes(
  fill = (Kessler5),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 5 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel restless or fidgety")

Kessler5.fit = glm(PetOwner ~ Kessler5, family = binomial, data = turk)
kable(summary(Kessler5.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
## *"During the past two weeks, how often did you feel so restless that you could not sit still?"*
```{r kessler6, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Kessler6 <-
  factor(
    turk$Kessler6,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
t6 <- table(turk$PetOwner, turk$Kessler6)
kable(t6, caption = "Contingency Table for Kessler 6 responces and Pet Ownership")

Kessler6 <-
  turk %>% group_by(PetOwner, Kessler6) %>% summarise(Frequency = length(Kessler6))
ggplot(Kessler6, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler6
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 6 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel so restless that you could not sit still")

ggplot(Kessler6, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler6
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 6 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel so restless that you could not sit still")

ggplot(Kessler6, aes(
  fill = (Kessler6),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 6 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel so restless that you could not sit still")

Kessler6.fit = glm(PetOwner ~ Kessler6, family = binomial, data = turk)
kable(summary(Kessler6.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often did you feel depressed??"*
```{r kessler7, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Kessler7 <-
  factor(
    turk$Kessler7,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
t7 <- table(turk$PetOwner, turk$Kessler7)
kable(t7, caption = "Contingency Table for Kessler 7 responces and Pet Ownership")

Kessler7 <-
  turk %>% group_by(PetOwner, Kessler7) %>% summarise(Frequency = length(Kessler7))
ggplot(Kessler7, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler7
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 7 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel depressed?")

ggplot(Kessler7, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler7
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 7 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel depressed?")

ggplot(Kessler7, aes(
  fill = (Kessler7),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 7 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel depressed?")

Kessler7.fit = glm(PetOwner ~ Kessler7, family = binomial, data = turk)
kable(summary(Kessler7.fit)$coef, digits = 2)
```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often did you feel so depressed that nothing could cheer you up?"*
```{r kessler8, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <- factor(turk$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk$Kessler8 <- factor(turk$Kessler8, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time"))

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
t8 <- table(turk$PetOwner, turk$Kessler8)
kable(t8, caption = "Contingency Table for Kessler 8 responces and Pet Ownership")

Kessler8 <-turk %>%group_by(PetOwner, Kessler8)%>%summarise(Frequency =length(Kessler8)) 
ggplot(Kessler8, aes(fill= (PetOwner), y=Frequency, x=Kessler8)) + 
geom_bar(position="dodge", stat="identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Kessler 8 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you / feel so depressed that nothing could cheer you up?")

ggplot(Kessler8, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler8
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 8 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you / feel so depressed that nothing could cheer you up?")

ggplot(Kessler8, aes(
  fill = (Kessler8),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 8 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you / feel so depressed that nothing could cheer you up?")

Kessler8.fit=glm(PetOwner~Kessler8,family=binomial,data=turk)
kable(summary(Kessler8.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often did you feel that everything was an effort?"*
```{r kessler9, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <- factor(turk$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk$Kessler9 <- factor(turk$Kessler9, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time"))

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
t9 <- table(turk$PetOwner, turk$Kessler9)
kable(t9, caption = "Contingency Table for Kessler 9 responces and Pet Ownership")

Kessler9 <-turk %>%group_by(PetOwner, Kessler9)%>%summarise(Frequency =length(Kessler9)) 
ggplot(Kessler9, aes(fill= (PetOwner), y=Frequency, x=Kessler9)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Kessler 9 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel that everything was an effort??")


ggplot(Kessler9, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler9
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 9 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel that everything was an effort??")

ggplot(Kessler9, aes(
  fill = (Kessler9),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
ggtitle("Frequency distribution of Kessler 9 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel that everything was an effort??")

Kessler9.fit=glm(PetOwner~Kessler9,family=binomial,data=turk)
kable(summary(Kessler9.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often did you feel worthless?"*

```{r kessler10, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <- factor(turk$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk$Kessler10 <- factor(turk$Kessler10, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time"))

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
t10 <- table(turk$PetOwner, turk$Kessler10)
kable(t10, caption = "Contingency Table for Kessler 10 responces and Pet Ownership")

Kessler10 <-turk %>%group_by(PetOwner, Kessler10)%>%summarise(Frequency =length(Kessler10)) 
ggplot(Kessler10, aes(fill= (PetOwner), y=Frequency, x=Kessler10)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Kessler 10 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel worthless??")


ggplot(Kessler10, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler10
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
ggtitle("Frequency distribution of Kessler 10 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel worthless??")

ggplot(Kessler10, aes(
  fill = (Kessler10),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
ggtitle("Frequency distribution of Kessler 10 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel worthless??")

Kessler10.fit=glm(PetOwner~Kessler10,family=binomial,data=turk)
kable(summary(Kessler10.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often have you been bothered by feeling nervous, anxious or on edge?"*
```{r Gad1, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Gad1 <-
  factor(
    turk$Gad1,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tGad1 <- table(turk$PetOwner, turk$Gad1)
kable(tGad1, caption = "Contingency Table for Gad1 responces and Pet Ownership")

Gad1 <-
  turk %>% group_by(PetOwner, Gad1) %>% summarise(Frequency = length(Gad1))
ggplot(Gad1, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad1
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad1 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often have you been bothered by feeling nervous, anxious or on edge?")
Gad1.fit = glm(PetOwner ~ Gad1, family = binomial, data = turk)
kable(summary(Gad1.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often have you been bothered by not being able to stop or control worrying?"*

```{r Gad2, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Gad2 <-
  factor(
    turk$Gad2,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tGad2 <- table(turk$PetOwner, turk$Gad2)
kable(tGad2, caption = "Contingency Table for Gad2 responces and Pet Ownership")

Gad2 <-
  turk %>% group_by(PetOwner, Gad2) %>% summarise(Frequency = length(Gad2))
ggplot(Gad2, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad2
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad2 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question:During the past two weeks, how often have you been bothered by not being able to stop or control worrying?")
Gad2.fit = glm(PetOwner ~ Gad2, family = binomial, data = turk)
kable(summary(Gad2.fit)$coef, digits = 2)


```

<div style="margin-bottom:100px;">
### During the past two weeks, how often have you been bothered by worrying too much about different things?
```{r Gad3, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Gad3 <-
  factor(
    turk$Gad3,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tGad3 <- table(turk$PetOwner, turk$Gad3)
kable(tGad3, caption = "Contingency Table for Gad3 responces and Pet Ownership")

Gad3 <-
  turk %>% group_by(PetOwner, Gad3) %>% summarise(Frequency = length(Gad3))
ggplot(Gad3, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad3
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad3 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question:During the past two weeks, how often have you been bothered by worrying too much about different things??")

Gad3.fit = glm(PetOwner ~ Gad3, family = binomial, data = turk)
kable(summary(Gad3.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often have you had trouble relaxing?
```{r Gad4, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Gad4 <-
  factor(
    turk$Gad4,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tGad4 <- table(turk$PetOwner, turk$Gad4)
kable(tGad4, caption = "Contingency Table for Gad4 responces and Pet Ownership")

Gad4 <-
  turk %>% group_by(PetOwner, Gad4) %>% summarise(Frequency = length(Gad4))
ggplot(Gad4, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad4
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad4 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often have you had trouble relaxing??")

Gad4.fit = glm(PetOwner ~ Gad4, family = binomial, data = turk)
kable(summary(Gad4.fit)$coef, digits = 2)
```

<div style="margin-bottom:100px;">
### During the past two weeks, how often have you had trouble relaxing?
```{r Gad5, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Gad5 <-
  factor(
    turk$Gad5,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tGad5 <- table(turk$PetOwner, turk$Gad5)
kable(tGad5, caption = "Contingency Table for Gad5 responces and Pet Ownership")

Gad5 <-
  turk %>% group_by(PetOwner, Gad5) %>% summarise(Frequency = length(Gad5))
ggplot(Gad5, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad5
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad5 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often have you had trouble relaxing??")
Gad5.fit = glm(PetOwner ~ Gad5, family = binomial, data = turk)
kable(summary(Gad5.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often have you become easily annoyed or irritable??
```{r Gad6, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Gad6 <-
  factor(
    turk$Gad6,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tGad6 <- table(turk$PetOwner, turk$Gad6)
kable(tGad6, caption = "Contingency Table for Gad6 responces and Pet Ownership")

Gad6 <-
  turk %>% group_by(PetOwner, Gad6) %>% summarise(Frequency = length(Gad6))
ggplot(Gad6, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad6
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad6 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often have you become easily annoyed or irritable?")
Gad6.fit = glm(PetOwner ~ Gad6, family = binomial, data = turk)
kable(summary(Gad6.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often have you been bothered by feeling afraid as if something awful might happen??
```{r Gad7, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Gad7 <-
  factor(
    turk$Gad7,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tGad7 <- table(turk$PetOwner, turk$Gad7)
kable(tGad7, caption = "Contingency Table for Gad7 responces and Pet Ownership")

Gad7 <-
  turk %>% group_by(PetOwner, Gad7) %>% summarise(Frequency = length(Gad7))
ggplot(Gad7, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad7
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad7 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question:During the past two weeks, how often have you been bothered by feeling afraid as if something awful might happen?")

Gad7.fit = glm(PetOwner ~ Gad7, family = binomial, data = turk)
kable(summary(Gad7.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### Paying attention?
```{r Q66, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Q66 <-
  factor(
    turk$Q66,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tQ66 <- table(turk$PetOwner, turk$Q66)
kable(tQ66, caption = "Contingency Table for Q66 responces and Pet Ownership")

Q66 <-
  turk %>% group_by(PetOwner, Q66) %>% summarise(Frequency = length(Q66))
ggplot(Q66, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Q66
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Q66 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question:Paying Attention")

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often did you feel you lack companionship??
```{r Lonely1, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Lonely1 <-
  factor(
    turk$Lonely1,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tLonely1 <- table(turk$PetOwner, turk$Lonely1)
kable(tLonely1, caption = "Contingency Table for Lonely1 responces and Pet Ownership")

Lonely1 <-
  turk %>% group_by(PetOwner, Lonely1) %>% summarise(Frequency = length(Lonely1))
ggplot(Lonely1, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Lonely1
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Lonely1 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel you lack companionship?")
Lonely1.fit = glm(PetOwner ~ Lonely1, family = binomial, data = turk)
kable(summary(Lonely1.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often did you feel left out??
```{r Lonely2, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <- factor(turk$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk$Lonely2 <- factor(turk$Lonely2, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time"))

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tLonely2 <- table(turk$PetOwner, turk$Lonely2)
kable(tLonely2, caption = "Contingency Table for Lonely2 responces and Pet Ownership")

Lonely2 <-turk %>%group_by(PetOwner, Lonely2)%>%summarise(Frequency =length(Lonely2)) 
ggplot(Lonely2, aes(fill= (PetOwner), y=Frequency, x=Lonely2)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Lonely2 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question:During the past two weeks, how often did you feel left out?")

Lonely2.fit=glm(PetOwner~Lonely1,family=binomial,data=turk)
kable(summary(Lonely2.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often did you feel isolated from others?
```{r Lonely3, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <- factor(turk$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk$Lonely3 <- factor(turk$Lonely3, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time"))

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tLonely3 <- table(turk$PetOwner, turk$Lonely3)
kable(tLonely3, caption = "Contingency Table for Lonely3 responces and Pet Ownership")

Lonely3 <-turk %>%group_by(PetOwner, Lonely3)%>%summarise(Frequency =length(Lonely3)) 
ggplot(Lonely3, aes(fill= (PetOwner), y=Frequency, x=Lonely3)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Lonely3 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question:During the past two weeks, how often did you feel isolated from others")

Lonely3.fit=glm(PetOwner~Lonely3,family=binomial,data=turk)
kable(summary(Lonely3.fit)$coef, digits=2)

```

#### Risk questions

<div style="margin-bottom:100px;">
### RISK 1: In your opinion, how likely is it that you will contract COVID-19?        ?
```{r Risk1, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <- factor(turk$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk$Risk1 <- factor(turk$Risk1, levels = c("1","2", "3","4","5","6", "7"), labels = c("Extremely unlikely", "Moderately unlikely","Slightly unlikely", "Neither likely nor unlikely", "Slightly likely", "Moderately likely", "Extremely likely"))


#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tRisk1 <- table(turk$PetOwner, turk$Risk1)
kable(tRisk1, caption = "Contingency Table for Risk1 responces and Pet Ownership")

Risk1 <-turk %>%group_by(PetOwner, Risk1)%>%summarise(Frequency =length(Risk1)) 
ggplot(Risk1, aes(fill= (PetOwner), y=Frequency, x=Risk1)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Risk1 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question:During the past two weeks, how often did you feel left out?")

Risk1.fit=glm(PetOwner~Risk1,family=binomial,data=turk)
kable(summary(Risk1.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### RISK 2: How serious do you think COVID-19 would be if you contracted it?        ?
```{r Risk2, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <- factor(turk$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk$Risk2 <- factor(turk$Risk2, levels = c("1","2", "3","4","5"), labels = c("Not at all", "Slightly","Moderately", "Very", "Extremely"))

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tRisk2 <- table(turk$PetOwner, turk$Risk2)
kable(tRisk2, caption = "Contingency Table for Risk2 responces and Pet Ownership")

Risk2 <-turk %>%group_by(PetOwner, Risk2)%>%summarise(Frequency =length(Risk2)) 
ggplot(Risk2, aes(fill= (PetOwner), y=Frequency, x=Risk2)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Risk2 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question:How serious do you think COVID-19 would be if you contracted it?")

Risk2.fit=glm(PetOwner~Risk2,family=binomial,data=turk)
kable(summary(Risk2.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### RISK 3: How concerned are you about the COVID-19??        ?
```{r Risk3, echo=F, warning=F} 
library(dplyr)
library(xtable)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
#turk$PetOwner<-as.factor(turk$PetOwner)
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Risk3 <-
  factor(
    turk$Risk3,
    levels = c("1", "2", "3", "4", "5"),
    labels = c("Not at all", "Slightly", "Moderately", "Very", "Extremely")
  )

#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tRisk3 <- table(turk$PetOwner, turk$Risk3)
kable(tRisk3, caption = "Contingency Table for Risk3 responces and Pet Ownership")

Risk3 <-
  turk %>% group_by(PetOwner, Risk3) %>% summarise(Frequency = length(Risk3))
ggplot(Risk3, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Risk3
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Risk3 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: How concerned are you about the COVID-19??")

Risk3.fit = glm(PetOwner ~ Risk3, family = binomial, data = turk)
kable(summary(Risk3.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### Pets2: How long have you had this animal?        ?
```{r Pets2, echo=F, warning=F} 
library(dplyr)
library(forcats)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Risk2 <-
  factor(
    turk$Risk2,
    levels = c("1", "2", "3", "4", "5"),
    labels = c("Not at all", "Slightly", "Moderately", "Very", "Extremely"),
    fct_explicit_na("Missing")
  )
turk$MostAttachTime <-
  factor(
    turk$MostAttachTime,
    levels = c("1", "2", "3"),
    labels = c("<1 month", "1-12 month", "more than 12 months"),
    fct_explicit_na("Missing")
  )
turk$MostAttach <-
  factor(
    turk$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#fct_explicit_na(turk$MostAttach,"Missing")
#fct_explicit_na(turk$PetOwner, na_level = "(Missing)")
tPets2 <- table(turk$MostAttachTime, turk$MostAttach)
kable(tPets2,
      caption = "Contingency Table for length of ownership",
      table.attr = "class=\"striped\"",
      format = "html")
# want to remove NA i.e. non pet owners.

MostAttachTime <- turk %>%
  dplyr::filter(PetOwner == "Pets=Yes") %>%
  group_by(MostAttachTime, MostAttach) %>% summarise(Frequency = length(MostAttachTime))


ggplot(MostAttachTime, aes(
  fill = (MostAttach),
  y = Frequency,
  x = MostAttachTime
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 45
    )
  ) +
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Question: How long have you owned your pet?")

```

<div style="margin-bottom:100px;">
### Compliance: How long have you had this animal?        
```{r Compliance, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Compliance <-
  factor(turk$Compliance,
         levels = c("0", "1"),
         labels = c("No", "Yes"))
turk$MostAttach <-
  factor(
    turk$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk$MostAttach<-factor(turk$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tCompliance <- table(turk$Compliance, turk$MostAttach)
kable(tCompliance, caption = "Contingency Table for All Pets and Quarantine Compliance")

Compliance <- turk %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(Compliance, MostAttach) %>%
  summarise(Frequency = length(Compliance))

ggplot(Compliance, aes(
  fill = (MostAttach),
  y = Frequency,
  x = Compliance
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Question:How has your complcaince been?")

ggplot(Compliance, aes(
  fill = (Compliance),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Question:How has your complcaince been?")

Compliance.fit = glm(Compliance ~ MostAttach, family = binomial, data =
                       turk)
kable(summary(Compliance.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### Interact: Has COVID-19 affected your normal activities and interactions with your pet/companion animal(s)?       
```{r Interact, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Interact <-
  factor(turk$Interact,
         levels = c("0", "1"),
         labels = c("No", "Yes"))
turk$MostAttach <-
  factor(
    turk$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk$MostAttach<-factor(turk$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tInteract <- table(turk$Interact, turk$MostAttach)
kable(tCompliance, caption = "Contingency Table for All Pets and Interaction")

Interact <- turk %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(Interact, MostAttach) %>%
  summarise(Frequency = length(Interact))

ggplot(Interact, aes(
  fill = (MostAttach),
  y = Frequency,
  x = Interact
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Interaction by pet") +
  labs(y = "Freqency of Responces", x = "Question:How has your complcaince been?")

ggplot(Interact, aes(
  fill = (Interact),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Question: Has COVID-19 affected your normal activities and interactions with your pet/companion animal(s)")

Interact.fit = glm(Interact ~ MostAttach, family = binomial, data =
                       turk)
kable(summary(Interact.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### Plans: Since the COVID-19 outbreak, have you made plans for caring for your pet/companion animal(s) should you become sick and unable to care for them?       
```{r Plans, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Plans <-
  factor(turk$Plans,
         levels = c("0", "1"),
         labels = c("No", "Yes"))
turk$MostAttach <-
  factor(
    turk$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk$MostAttach<-factor(turk$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tPlans <- table(turk$Plans, turk$MostAttach)
kable(tCompliance, caption = "Contingency Table for All Pets and Plans")

Plans <- turk %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(Plans, MostAttach) %>%
  summarise(Frequency = length(Plans))

ggplot(Plans, aes(
  fill = (MostAttach),
  y = Frequency,
  x = Plans
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Plans by pet") +
  labs(y = "Frequency of Responces", x = "QPlans")

ggplot(Plans, aes(
  fill = (Plans),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Since the COVID-19 outbreak, have you made plans for caring for your pet/companion animal(s) should you become sick and unable to care for them?" )

Plans.fit = glm(Plans ~ MostAttach, family = binomial, data =
                       turk)
kable(summary(Plans.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### Concern: Overall, how concerned are you about your ability to care for your pets/companion animal(s)?       
```{r Concern, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$Concern <-
  factor(turk$Concern,
         levels = c("1", "2","3","4","5"),
         labels = c("Not at all concerned", "A little concerned", "Moderately concerened", "Very concerned", "Extremely concerned"))


turk$MostAttach <-
  factor(
    turk$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk$MostAttach<-factor(turk$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tPlans <- table(turk$Concern, turk$MostAttach)
kable(tCompliance, caption = "Contingency Table for All Pets and Concerns")

Concern <- turk %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(Concern, MostAttach) %>%
  summarise(Frequency = length(Concern))

ggplot(Concern, aes(
  fill = (MostAttach),
  y = Frequency,
  x = Concern
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Concerns by pet") +
  labs(y = "Frequency of Responces", x = "Concerns")

ggplot(Concern, aes(
  fill = (Concern),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Since the COVID-19 outbreak, have you made plans for caring for your pet/companion animal(s) should you become sick and unable to care for them?" )

Concern.fit = glm(Concern ~ MostAttach, family = binomial, data =
                       turk)
kable(summary(Concern.fit)$coef, digits = 2)

```


<div style="margin-bottom:100px;">
### CCAS1: My pet/animal provides me with companionship?       
```{r CCAS1, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$CCAS1 <-
  factor(turk$CCAS1,
         levels = c("1", "2","3","4","5","6","7"),
         labels = c(
           "Strongly disagree",
           "Disagree" ,
           "Somewhat disagree",
           "Neither agree nor disagree", 
          "Somewhat agree", 
          "Agree", 
          "Strongly agree" 
))


turk$MostAttach <-
  factor(
    turk$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk$MostAttach<-factor(turk$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tCCAS1 <- table(turk$CCAS1, turk$MostAttach)
kable(tCCAS1, caption = "CCAS1: My pet/animal provides me with companionship?")

CCAS1 <- turk %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(CCAS1, MostAttach) %>%
  summarise(Frequency = length(CCAS1))

ggplot(CCAS1, aes(
  fill = (MostAttach),
  y = Frequency,
  x = CCAS1
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of CCAS1 by pet") +
  labs(y = "Frequency of Responces", x = "My pet/animal provides me with companionship?")

ggplot(CCAS1, aes(
  fill = (CCAS1),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "My pet/animal provides me with companionship?" )

CCAS1.fit = glm(CCAS1 ~ MostAttach, family = binomial, data =
                       turk)
kable(summary(CCAS1.fit)$coef, digits = 2)

```









<div style="margin-bottom:100px;">




### CCAS2: Having a pet/animal gives me something to care for?  
```{r CCAS2, echo=F, warning=F} 
library(dplyr)
turk <- read_excel("2020-4-17 COVID_Raw_Data.xls")
turk$PetOwner <-
  factor(
    turk$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk$CCAS2 <-
  factor(turk$CCAS2,
         levels = c("1", "2","3","4","5","6","7"),
         labels = c(
           "Strongly disagree",
           "Disagree" ,
           "Somewhat disagree",
           "Neither agree nor disagree", 
          "Somewhat agree", 
          "Agree", 
          "Strongly agree" 
))


turk$MostAttach <-
  factor(
    turk$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk$MostAttach<-factor(turk$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tCCAS2 <- table(turk$CCAS2, turk$MostAttach)
kable(tCCAS2, caption = "CCAS2: Having a pet/animal gives me something to care for")

CCAS2 <- turk %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(CCAS2, MostAttach) %>%
  summarise(Frequency = length(CCAS2))

ggplot(CCAS2, aes(
  fill = (MostAttach),
  y = Frequency,
  x = CCAS2
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of CCAS2 by pet") +
  labs(y = "Frequency of Responces", x = "Having a pet/animal gives me something to care for")

ggplot(CCAS2, aes(
  fill = (CCAS2),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Having a pet/animal gives me something to care for?" )

CCAS2.fit = glm(CCAS2 ~ MostAttach, family = binomial, data =
                       turk)
kable(summary(CCAS2.fit)$coef, digits = 2)

```







# {Wave 2 specific questions}
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")

## {Basic Description of the Participants}

```{r turk2figur1,echo = FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(knitr)
library(xtable)
#importing the data and arranging properly
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
numResponces<-nrow(turk2)
#frequency grouped by outcomes and year
###Table 1
pets <- turk2 %>% group_by(PetOwner)
## of reported pets
numPET <-  turk2 %>%
            dplyr::filter(PetOwner == 1) %>%
            tally() %>%
            .[,"n"]
numDOG <-  turk2 %>%
            dplyr::filter(PetOwner == 1, PetTypes_1 != 0) %>%
            tally() %>%
            .[,"n"]
numCAT <-  turk2 %>%
            dplyr::filter(PetOwner == 1, PetTypes_2 != 0) %>%
            tally() %>%
            .[,"n"]
numHORSE <-  turk2 %>%
            dplyr::filter(PetOwner == 1, PetTypes_3 != 0) %>%
            tally() %>%
            .[,"n"]
numBIRD <-  turk2 %>%
            dplyr::filter(PetOwner == 1, PetTypes_4 != 0) %>%
            tally() %>%
            .[,"n"]
numREPTILE <-  turk2 %>%
            dplyr::filter(PetOwner == 1, PetTypes_5 != 0) %>%
            tally() %>%
            .[,"n"]
numSM <-  turk2 %>%
            dplyr::filter(PetOwner == 1, PetTypes_6 != 0) %>%
            tally() %>%
            .[,"n"]
numFISH <-  turk2 %>%
            dplyr::filter(PetOwner == 1, PetTypes_7 != 0) %>%
            tally() %>%
            .[,"n"]
numOTHER <-  turk2 %>%
            dplyr::filter(PetOwner == 1, PetTypes_8 != 0) %>%
            tally() %>%
            .[,"n"]
numDOGCAT <-  turk2 %>%
            dplyr::filter(PetOwner == 1, PetTypes_1 != 0, PetTypes_2 !=0) %>%
            tally() %>%
            .[,"n"]
propPET<-round((numPET/numResponces)*100,1)
propDOG<-round((numDOG/numPET)*100,1)
propCAT<-round((numCAT/numPET)*100,1)
propHORSE<-round((numHORSE/numPET)*100,1)
propFISH<-round((numFISH/numPET)*100,1)
propREPTILE<-round((numREPTILE/numPET)*100,1)
propOTHER<-round((numOTHER/numPET)*100,1)
propSM<-round((numSM/numPET)*100,1)
propDOGCAT<-round((numDOGCAT/numPET)*100,1)
```
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

The survey was conducted in April 2020, and `r numResponces` responces were obtained. Of these `r numResponces` respondents, `r numPET` reporting owning pets (`r propPET`%).  Of the pet owners,  `r numDOG` (`r propDOG`%) reported owning dogs, `r numCAT`(`r propCAT`%) reported owning cats, `r numHORSE`(`r propHORSE`%) reported owning horses, `r numREPTILE` (`r propREPTILE`%) reporting owning reptiles, `r numSM` (`r propSM`%) reporting owning small mammals, `r numFISH` (`r propFISH`%) reporting owning fish and `r numOTHER`(`r propOTHER`%) reported owning other animals. `r numDOGCAT` reported owning both cats and dogs.  

```{r turk2tables, results="asis"}
library(xtable)
library(broom)
X <- summary(turk2$age)
X <- tidy(X)
kable(X,
      align = "rrrrr",
      caption = "Summary characteritics for age.",
      digits = 0)
mean_age<-round(X[4],0)
med_age<-round(X[3],0)
#col.names = c("min", "Quart1", "med", "mean", "Qurt 3", "max"),

```
<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

The mean age of particiants was `r mean_age` and the median was `r med_age`.

## Kessler responces for the participants

### During the past two weeks, how often did you feel tired for no good reason?

```{r turk2kessler1, echo=F, warning=F} 
library(dplyr)

library(forcats)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Kessler1 <-
  factor(
    turk2$Kessler1,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#turk2$PetOwner <- factor(turk2$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes")) %>% fct_explicit_na("Missing")
#$turk2$Kessler1 <- factor(turk2$Kessler1, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time")) %>% fct_explicit_na("Missing")
Kessler1 <-
  turk2 %>% group_by(PetOwner, Kessler1) %>% summarise(Frequency = length(Kessler1))
t1 <- table(turk2$PetOwner, turk2$Kessler1)
kable(t1, caption = "Contingency table for Kessler 1 responces and Pet Ownership")
ggplot(Kessler1, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler1
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 1 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel tired for no good reason?")

ggplot(Kessler1, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler1
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 1 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel tired for no good reason?")
#making tables


ggplot(Kessler1, aes(
  fill = (Kessler1),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 1 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel tired for no good reason?")
#making tables


Kessler1.fit = glm(PetOwner ~ Kessler1, family = binomial, data = turk2)
kable(summary(Kessler1.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
###  "During the past two weeks, how often did you feel nervous? 
```{r turk2kessler2, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Kessler2 <-
  factor(
    turk2$Kessler2,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )
#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")

t2 <- table(turk2$PetOwner, turk2$Kessler2)
kable(t2, caption = "Contingency Table for Kessler 2 responces and Pet Ownership")

Kessler2 <-
  turk2 %>% group_by(PetOwner, Kessler2) %>% summarise(Frequency = length(Kessler2))

ggplot(Kessler2, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler2
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 2 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often did you feel nervous?")

ggplot(Kessler2, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler2
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 2 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often did you feel nervous?")
#making tables

ggplot(Kessler2, aes(
  fill = (Kessler2),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 2 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel nervous?")

Kessler2.fit = glm(PetOwner ~ Kessler2, family = binomial, data = turk2)
kable(summary(Kessler2.fit)$coef, digits = 2)
```

<div style="margin-bottom:100px;">
## "During the past two weeks, how often did you feel so nervous that nothing could calm you down??"
```{r turk2kessler3, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Kessler3 <-
  factor(
    turk2$Kessler3,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
t3 <- table(turk2$PetOwner, turk2$Kessler3)
kable(t3, caption = "Contingency Table for Kessler 3 responces and Pet Ownership")

Kessler3 <-
  turk2 %>% group_by(PetOwner, Kessler3) %>% summarise(Frequency = length(Kessler3))
ggplot(Kessler3, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler3
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 3 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often \ did you feel so nervous that nothing could calm you down??")


ggplot(Kessler3, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler3
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 3 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often \ did you feel so nervous that nothing could calm you down??")



ggplot(Kessler3, aes(
  fill = (Kessler3),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 3 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often \ did you feel so nervous that nothing could calm you down??")


Kessler3.fit = glm(PetOwner ~ Kessler3, family = binomial, data = turk2)
kable(summary(Kessler3.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
## "During the past two weeks, how often did you feel hopeless?"
```{r turk2kessler4, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Kessler4 <-
  factor(
    turk2$Kessler4,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
t4 <- table(turk2$PetOwner, turk2$Kessler4)
kable(t4, caption = "Contingency Table for Kessler 4 responces and Pet Ownership")

Kessler4 <-
  turk2 %>% group_by(PetOwner, Kessler4) %>% summarise(Frequency = length(Kessler4))
ggplot(Kessler4, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler4
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 4 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often did you feel hopeless?")

ggplot(Kessler4, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler4
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 4 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often did you feel hopeless?")

ggplot(Kessler4, aes(
  fill = (Kessler4),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 4 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "During the past two weeks, how often did you feel hopeless?")

Kessler4.fit = glm(PetOwner ~ Kessler4, family = binomial, data = turk2)
kable(summary(Kessler4.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
## *"During the past two weeks, how often did you feel restless or fidgety?"*
```{r turk2kessler5, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Kessler5 <-
  factor(
    turk2$Kessler5,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
t5 <- table(turk2$PetOwner, turk2$Kessler5)
kable(t5, caption = "Contingency Table for Kessler 5 responces and Pet Ownership")

Kessler5 <-
  turk2 %>% group_by(PetOwner, Kessler5) %>% summarise(Frequency = length(Kessler5))
ggplot(Kessler5, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler5
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 5 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel restless or fidgety")

ggplot(Kessler5, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler5
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 5 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel restless or fidgety")

ggplot(Kessler5, aes(
  fill = (Kessler5),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 5 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel restless or fidgety")

Kessler5.fit = glm(PetOwner ~ Kessler5, family = binomial, data = turk2)
kable(summary(Kessler5.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
## *"During the past two weeks, how often did you feel so restless that you could not sit still?"*
```{r turk2kessler6, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Kessler6 <-
  factor(
    turk2$Kessler6,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
t6 <- table(turk2$PetOwner, turk2$Kessler6)
kable(t6, caption = "Contingency Table for Kessler 6 responces and Pet Ownership")

Kessler6 <-
  turk2 %>% group_by(PetOwner, Kessler6) %>% summarise(Frequency = length(Kessler6))
ggplot(Kessler6, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler6
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 6 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel so restless that you could not sit still")

ggplot(Kessler6, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler6
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 6 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel so restless that you could not sit still")

ggplot(Kessler6, aes(
  fill = (Kessler6),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 6 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel so restless that you could not sit still")

Kessler6.fit = glm(PetOwner ~ Kessler6, family = binomial, data = turk2)
kable(summary(Kessler6.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often did you feel depressed??"*
```{r turk2kessler7, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Kessler7 <-
  factor(
    turk2$Kessler7,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
t7 <- table(turk2$PetOwner, turk2$Kessler7)
kable(t7, caption = "Contingency Table for Kessler 7 responces and Pet Ownership")

Kessler7 <-
  turk2 %>% group_by(PetOwner, Kessler7) %>% summarise(Frequency = length(Kessler7))
ggplot(Kessler7, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler7
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 7 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel depressed?")

ggplot(Kessler7, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler7
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 7 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel depressed?")

ggplot(Kessler7, aes(
  fill = (Kessler7),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 7 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel depressed?")

Kessler7.fit = glm(PetOwner ~ Kessler7, family = binomial, data = turk2)
kable(summary(Kessler7.fit)$coef, digits = 2)
```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often did you feel so depressed that nothing could cheer you up?"*
```{r turk22kessler8, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <- factor(turk2$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk2$Kessler8 <- factor(turk2$Kessler8, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time"))

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
t8 <- table(turk2$PetOwner, turk2$Kessler8)
kable(t8, caption = "Contingency Table for Kessler 8 responces and Pet Ownership")

Kessler8 <-turk2 %>%group_by(PetOwner, Kessler8)%>%summarise(Frequency =length(Kessler8)) 
ggplot(Kessler8, aes(fill= (PetOwner), y=Frequency, x=Kessler8)) + 
geom_bar(position="dodge", stat="identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Kessler 8 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you / feel so depressed that nothing could cheer you up?")

ggplot(Kessler8, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler8
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 8 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you / feel so depressed that nothing could cheer you up?")

ggplot(Kessler8, aes(
  fill = (Kessler8),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 8 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you / feel so depressed that nothing could cheer you up?")

Kessler8.fit=glm(PetOwner~Kessler8,family=binomial,data=turk2)
kable(summary(Kessler8.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often did you feel that everything was an effort?"*
```{r turk2kessler9, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <- factor(turk2$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk2$Kessler9 <- factor(turk2$Kessler9, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time"))

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
t9 <- table(turk2$PetOwner, turk2$Kessler9)
kable(t9, caption = "Contingency Table for Kessler 9 responces and Pet Ownership")

Kessler9 <-turk2 %>%group_by(PetOwner, Kessler9)%>%summarise(Frequency =length(Kessler9)) 
ggplot(Kessler9, aes(fill= (PetOwner), y=Frequency, x=Kessler9)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Kessler 9 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel that everything was an effort??")


ggplot(Kessler9, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler9
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Kessler 9 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel that everything was an effort??")

ggplot(Kessler9, aes(
  fill = (Kessler9),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
ggtitle("Frequency distribution of Kessler 9 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel that everything was an effort??")

Kessler9.fit=glm(PetOwner~Kessler9,family=binomial,data=turk2)
kable(summary(Kessler9.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often did you feel worthless?"*

```{r turk2kessler10, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <- factor(turk2$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk2$Kessler10 <- factor(turk2$Kessler10, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time"))

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
t10 <- table(turk2$PetOwner, turk2$Kessler10)
kable(t10, caption = "Contingency Table for Kessler 10 responces and Pet Ownership")

Kessler10 <-turk2 %>%group_by(PetOwner, Kessler10)%>%summarise(Frequency =length(Kessler10)) 
ggplot(Kessler10, aes(fill= (PetOwner), y=Frequency, x=Kessler10)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Kessler 10 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel worthless??")


ggplot(Kessler10, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Kessler10
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
ggtitle("Frequency distribution of Kessler 10 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel worthless??")

ggplot(Kessler10, aes(
  fill = (Kessler10),
  y = Frequency,
  x = PetOwner
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
ggtitle("Frequency distribution of Kessler 10 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question: During the past two weeks, how often did you feel worthless??")

Kessler10.fit=glm(PetOwner~Kessler10,family=binomial,data=turk2)
kable(summary(Kessler10.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often have you been bothered by feeling nervous, anxious or on edge?"*
```{r turk2Gad1, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Gad1 <-
  factor(
    turk2$Gad1,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tGad1 <- table(turk2$PetOwner, turk2$Gad1)
kable(tGad1, caption = "Contingency Table for Gad1 responces and Pet Ownership")

Gad1 <-
  turk2 %>% group_by(PetOwner, Gad1) %>% summarise(Frequency = length(Gad1))
ggplot(Gad1, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad1
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad1 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often have you been bothered by feeling nervous, anxious or on edge?")
Gad1.fit = glm(PetOwner ~ Gad1, family = binomial, data = turk2)
kable(summary(Gad1.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### *"During the past two weeks, how often have you been bothered by not being able to stop or control worrying?"*

```{r turk22Gad2, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Gad2 <-
  factor(
    turk2$Gad2,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tGad2 <- table(turk2$PetOwner, turk2$Gad2)
kable(tGad2, caption = "Contingency Table for Gad2 responces and Pet Ownership")

Gad2 <-
  turk2 %>% group_by(PetOwner, Gad2) %>% summarise(Frequency = length(Gad2))
ggplot(Gad2, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad2
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad2 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question:During the past two weeks, how often have you been bothered by not being able to stop or control worrying?")
Gad2.fit = glm(PetOwner ~ Gad2, family = binomial, data = turk2)
kable(summary(Gad2.fit)$coef, digits = 2)


```

<div style="margin-bottom:100px;">
### During the past two weeks, how often have you been bothered by worrying too much about different things?
```{r turk22Gad3, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Gad3 <-
  factor(
    turk2$Gad3,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tGad3 <- table(turk2$PetOwner, turk2$Gad3)
kable(tGad3, caption = "Contingency Table for Gad3 responces and Pet Ownership")

Gad3 <-
  turk2 %>% group_by(PetOwner, Gad3) %>% summarise(Frequency = length(Gad3))
ggplot(Gad3, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad3
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad3 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question:During the past two weeks, how often have you been bothered by worrying too much about different things??")

Gad3.fit = glm(PetOwner ~ Gad3, family = binomial, data = turk2)
kable(summary(Gad3.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often have you had trouble relaxing?
```{r turk22Gad4, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Gad4 <-
  factor(
    turk2$Gad4,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tGad4 <- table(turk2$PetOwner, turk2$Gad4)
kable(tGad4, caption = "Contingency Table for Gad4 responces and Pet Ownership")

Gad4 <-
  turk2 %>% group_by(PetOwner, Gad4) %>% summarise(Frequency = length(Gad4))
ggplot(Gad4, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad4
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad4 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often have you had trouble relaxing??")

Gad4.fit = glm(PetOwner ~ Gad4, family = binomial, data = turk2)
kable(summary(Gad4.fit)$coef, digits = 2)
```

<div style="margin-bottom:100px;">
### During the past two weeks, how often have you had trouble relaxing?
```{r turk22Gad5, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Gad5 <-
  factor(
    turk2$Gad5,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tGad5 <- table(turk2$PetOwner, turk2$Gad5)
kable(tGad5, caption = "Contingency Table for Gad5 responces and Pet Ownership")

Gad5 <-
  turk2 %>% group_by(PetOwner, Gad5) %>% summarise(Frequency = length(Gad5))
ggplot(Gad5, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad5
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad5 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often have you had trouble relaxing??")
Gad5.fit = glm(PetOwner ~ Gad5, family = binomial, data = turk2)
kable(summary(Gad5.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often have you become easily annoyed or irritable??
```{r turk22Gad6, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Gad6 <-
  factor(
    turk2$Gad6,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tGad6 <- table(turk2$PetOwner, turk2$Gad6)
kable(tGad6, caption = "Contingency Table for Gad6 responces and Pet Ownership")

Gad6 <-
  turk2 %>% group_by(PetOwner, Gad6) %>% summarise(Frequency = length(Gad6))
ggplot(Gad6, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad6
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad6 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often have you become easily annoyed or irritable?")
Gad6.fit = glm(PetOwner ~ Gad6, family = binomial, data = turk2)
kable(summary(Gad6.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often have you been bothered by feeling afraid as if something awful might happen??
```{r turk22Gad7, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Gad7 <-
  factor(
    turk2$Gad7,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tGad7 <- table(turk2$PetOwner, turk2$Gad7)
kable(tGad7, caption = "Contingency Table for Gad7 responces and Pet Ownership")

Gad7 <-
  turk2 %>% group_by(PetOwner, Gad7) %>% summarise(Frequency = length(Gad7))
ggplot(Gad7, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Gad7
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Gad7 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question:During the past two weeks, how often have you been bothered by feeling afraid as if something awful might happen?")

Gad7.fit = glm(PetOwner ~ Gad7, family = binomial, data = turk2)
kable(summary(Gad7.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### Paying attention?
```{r turk22Q66, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Q66 <-
  factor(
    turk2$Q66,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tQ66 <- table(turk2$PetOwner, turk2$Q66)
kable(tQ66, caption = "Contingency Table for Q66 responces and Pet Ownership")

Q66 <-
  turk2 %>% group_by(PetOwner, Q66) %>% summarise(Frequency = length(Q66))
ggplot(Q66, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Q66
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Q66 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question:Paying Attention")

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often did you feel you lack companionship??
```{r turk22Lonely1, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Lonely1 <-
  factor(
    turk2$Lonely1,
    levels = c("1", "2", "3", "4", "5"),
    labels = c(
      "None of the time",
      "A little of the time",
      "Some of the time",
      "Mostof the time",
      "All of the time"
    )
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tLonely1 <- table(turk2$PetOwner, turk2$Lonely1)
kable(tLonely1, caption = "Contingency Table for Lonely1 responces and Pet Ownership")

Lonely1 <-
  turk2 %>% group_by(PetOwner, Lonely1) %>% summarise(Frequency = length(Lonely1))
ggplot(Lonely1, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Lonely1
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Lonely1 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: During the past two weeks, how often did you feel you lack companionship?")
Lonely1.fit = glm(PetOwner ~ Lonely1, family = binomial, data = turk2)
kable(summary(Lonely1.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often did you feel left out??
```{r turk22Lonely2, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <- factor(turk2$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk2$Lonely2 <- factor(turk2$Lonely2, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time"))

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tLonely2 <- table(turk2$PetOwner, turk2$Lonely2)
kable(tLonely2, caption = "Contingency Table for Lonely2 responces and Pet Ownership")

Lonely2 <-turk2 %>%group_by(PetOwner, Lonely2)%>%summarise(Frequency =length(Lonely2)) 
ggplot(Lonely2, aes(fill= (PetOwner), y=Frequency, x=Lonely2)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Lonely2 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question:During the past two weeks, how often did you feel left out?")

Lonely2.fit=glm(PetOwner~Lonely1,family=binomial,data=turk2)
kable(summary(Lonely2.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### During the past two weeks, how often did you feel isolated from others?
```{r turk22Lonely3, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <- factor(turk2$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk2$Lonely3 <- factor(turk2$Lonely3, levels = c("1","2", "3","4","5"), labels = c("None of the time", "A little of the time","Some of the time", "Mostof the time", "All of the time"))

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tLonely3 <- table(turk2$PetOwner, turk2$Lonely3)
kable(tLonely3, caption = "Contingency Table for Lonely3 responces and Pet Ownership")

Lonely3 <-turk2 %>%group_by(PetOwner, Lonely3)%>%summarise(Frequency =length(Lonely3)) 
ggplot(Lonely3, aes(fill= (PetOwner), y=Frequency, x=Lonely3)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Lonely3 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question:During the past two weeks, how often did you feel isolated from others")

Lonely3.fit=glm(PetOwner~Lonely3,family=binomial,data=turk2)
kable(summary(Lonely3.fit)$coef, digits=2)

```

#### Risk questions

<div style="margin-bottom:100px;">
### RISK 1: In your opinion, how likely is it that you will contract COVID-19?        ?
```{r turk22Risk1, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <- factor(turk2$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk2$Risk1 <- factor(turk2$Risk1, levels = c("1","2", "3","4","5","6", "7"), labels = c("Extremely unlikely", "Moderately unlikely","Slightly unlikely", "Neither likely nor unlikely", "Slightly likely", "Moderately likely", "Extremely likely"))


#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tRisk1 <- table(turk2$PetOwner, turk2$Risk1)
kable(tRisk1, caption = "Contingency Table for Risk1 responces and Pet Ownership")

Risk1 <-turk2 %>%group_by(PetOwner, Risk1)%>%summarise(Frequency =length(Risk1)) 
ggplot(Risk1, aes(fill= (PetOwner), y=Frequency, x=Risk1)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Risk1 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question:During the past two weeks, how often did you feel left out?")

Risk1.fit=glm(PetOwner~Risk1,family=binomial,data=turk2)
kable(summary(Risk1.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### RISK 2: How serious do you think COVID-19 would be if you contracted it?        ?
```{r turk22Risk2, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <- factor(turk2$PetOwner, levels = c("0","1"), labels = c("Pets=No", "Pets=Yes"))
turk2$Risk2 <- factor(turk2$Risk2, levels = c("1","2", "3","4","5"), labels = c("Not at all", "Slightly","Moderately", "Very", "Extremely"))

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tRisk2 <- table(turk2$PetOwner, turk2$Risk2)
kable(tRisk2, caption = "Contingency Table for Risk2 responces and Pet Ownership")

Risk2 <-turk2 %>%group_by(PetOwner, Risk2)%>%summarise(Frequency =length(Risk2)) 
ggplot(Risk2, aes(fill= (PetOwner), y=Frequency, x=Risk2)) + 
geom_bar(position="dodge", stat="identity") +
theme(axis.text.x = element_text(face="bold", color="#993333", 
                           size=10, angle=90),
          axis.text.y = element_text(face="bold", color="#993333", 
                           size=10, angle=0)) +
ggtitle("Frequency distribution of Risk2 responces and Pet Ownership") +
labs(y="Freqency of Responces", x = "Question:How serious do you think COVID-19 would be if you contracted it?")

Risk2.fit=glm(PetOwner~Risk2,family=binomial,data=turk2)
kable(summary(Risk2.fit)$coef, digits=2)

```

<div style="margin-bottom:100px;">
### RISK 3: How concerned are you about the COVID-19??        ?
```{r turk22Risk3, echo=F, warning=F} 
library(dplyr)
library(xtable)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
#turk2$PetOwner<-as.factor(turk2$PetOwner)
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Risk3 <-
  factor(
    turk2$Risk3,
    levels = c("1", "2", "3", "4", "5"),
    labels = c("Not at all", "Slightly", "Moderately", "Very", "Extremely")
  )

#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tRisk3 <- table(turk2$PetOwner, turk2$Risk3)
kable(tRisk3, caption = "Contingency Table for Risk3 responces and Pet Ownership")

Risk3 <-
  turk2 %>% group_by(PetOwner, Risk3) %>% summarise(Frequency = length(Risk3))
ggplot(Risk3, aes(
  fill = (PetOwner),
  y = Frequency,
  x = Risk3
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Risk3 responces and Pet Ownership") +
  labs(y = "Freqency of Responces", x = "Question: How concerned are you about the COVID-19??")

Risk3.fit = glm(PetOwner ~ Risk3, family = binomial, data = turk2)
kable(summary(Risk3.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### Pets2: How long have you had this animal?        ?
```{r turk22Pets2, echo=F, warning=F} 
library(dplyr)
library(forcats)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Risk2 <-
  factor(
    turk2$Risk2,
    levels = c("1", "2", "3", "4", "5"),
    labels = c("Not at all", "Slightly", "Moderately", "Very", "Extremely"),
    fct_explicit_na("Missing")
  )
turk2$MostAttachTime <-
  factor(
    turk2$MostAttachTime,
    levels = c("1", "2", "3"),
    labels = c("<1 month", "1-12 month", "more than 12 months"),
    fct_explicit_na("Missing")
  )
turk2$MostAttach <-
  factor(
    turk2$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#fct_explicit_na(turk2$MostAttach,"Missing")
#fct_explicit_na(turk2$PetOwner, na_level = "(Missing)")
tPets2 <- table(turk2$MostAttachTime, turk2$MostAttach)
kable(tPets2,
      caption = "Contingency Table for length of ownership",
      table.attr = "class=\"striped\"",
      format = "html")
# want to remove NA i.e. non pet owners.

MostAttachTime <- turk2 %>%
  dplyr::filter(PetOwner == "Pets=Yes") %>%
  group_by(MostAttachTime, MostAttach) %>% summarise(Frequency = length(MostAttachTime))


ggplot(MostAttachTime, aes(
  fill = (MostAttach),
  y = Frequency,
  x = MostAttachTime
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 45
    )
  ) +
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Question: How long have you owned your pet?")

```

<div style="margin-bottom:100px;">
### Compliance: How long have you had this animal?        
```{r turk22Compliance, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Compliance <-
  factor(turk2$Compliance,
         levels = c("0", "1"),
         labels = c("No", "Yes"))
turk2$MostAttach <-
  factor(
    turk2$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk2$MostAttach<-factor(turk2$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tCompliance <- table(turk2$Compliance, turk2$MostAttach)
kable(tCompliance, caption = "Contingency Table for All Pets and Quarantine Compliance")

Compliance <- turk2 %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(Compliance, MostAttach) %>%
  summarise(Frequency = length(Compliance))

ggplot(Compliance, aes(
  fill = (MostAttach),
  y = Frequency,
  x = Compliance
)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Question:How has your complcaince been?")

ggplot(Compliance, aes(
  fill = (Compliance),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Question:How has your complcaince been?")

Compliance.fit = glm(Compliance ~ MostAttach, family = binomial, data =
                       turk2)
kable(summary(Compliance.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### Interact: Has COVID-19 affected your normal activities and interactions with your pet/companion animal(s)?       
```{r turk22Interact, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Interact <-
  factor(turk2$Interact,
         levels = c("0", "1"),
         labels = c("No", "Yes"))
turk2$MostAttach <-
  factor(
    turk2$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk2$MostAttach<-factor(turk2$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tInteract <- table(turk2$Interact, turk2$MostAttach)
kable(tInteract, caption = "Contingency Table for All Pets and Interaction")

Interact <- turk2 %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(Interact, MostAttach) %>%
  summarise(Frequency = length(Interact))

ggplot(Interact, aes(
  fill = (MostAttach),
  y = Frequency,
  x = Interact
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Interaction by pet") +
  labs(y = "Freqency of Responces", x = "Question:How has your complcaince been?")

ggplot(Interact, aes(
  fill = (Interact),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Question: Has COVID-19 affected your normal activities and interactions with your pet/companion animal(s)")

Interact.fit = glm(Interact ~ MostAttach, family = binomial, data =
                       turk2)
kable(summary(Interact.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### Plans: Since the COVID-19 outbreak, have you made plans for caring for your pet/companion animal(s) should you become sick and unable to care for them?       
```{r turk22Plans, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Plans <-
  factor(turk2$Plans,
         levels = c("0", "1"),
         labels = c("No", "Yes"))
turk2$MostAttach <-
  factor(
    turk2$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk2$MostAttach<-factor(turk2$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tPlans <- table(turk2$Plans, turk2$MostAttach)
kable(tPlans, caption = "Contingency Table for All Pets and Plans")

Plans <- turk2 %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(Plans, MostAttach) %>%
  summarise(Frequency = length(Plans))

ggplot(Plans, aes(
  fill = (MostAttach),
  y = Frequency,
  x = Plans
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Plans by pet") +
  labs(y = "Frequency of Responces", x = "QPlans")

ggplot(Plans, aes(
  fill = (Plans),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Since the COVID-19 outbreak, have you made plans for caring for your pet/companion animal(s) should you become sick and unable to care for them?" )

Plans.fit = glm(Plans ~ MostAttach, family = binomial, data =
                       turk2)
kable(summary(Plans.fit)$coef, digits = 2)

```

<div style="margin-bottom:100px;">
### Concern: Overall, how concerned are you about your ability to care for your pets/companion animal(s)?       
```{r turk22Concern, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$Concern <-
  factor(turk2$Concern,
         levels = c("1", "2","3","4","5"),
         labels = c("Not at all concerned", "A little concerned", "Moderately concerened", "Very concerned", "Extremely concerned"))


turk2$MostAttach <-
  factor(
    turk2$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk2$MostAttach<-factor(turk2$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tConcern <- table(turk2$Concern, turk2$MostAttach)
kable(tConcern, caption = "Contingency Table for All Pets and Concerns")

Concern <- turk2 %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(Concern, MostAttach) %>%
  summarise(Frequency = length(Concern))

ggplot(Concern, aes(
  fill = (MostAttach),
  y = Frequency,
  x = Concern
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of Concerns by pet") +
  labs(y = "Frequency of Responces", x = "Concerns")

ggplot(Concern, aes(
  fill = (Concern),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Since the COVID-19 outbreak, have you made plans for caring for your pet/companion animal(s) should you become sick and unable to care for them?" )

Concern.fit = glm(Concern ~ MostAttach, family = binomial, data =
                       turk2)
kable(summary(Concern.fit)$coef, digits = 2)

```


### NonVetService: In the past 12 months have you used an animal care service that does NOT normally require a veterinarian?         
```{r turk2NonVetService, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$NonVetService <-
  factor(
    turk2$NonVetService,
    levels = c("0", "1"),
    labels = c("No", "Yes")
  )

turk2$MostAttach <-
  factor(
    turk2$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )



tNonVetService <- table(turk2$NonVetService, turk2$MostAttach)
kable(tNonVetService, caption = "Contingency Table for  NonVetService")

NonVetService <- turk2 %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(NonVetService, MostAttach) %>%
  summarise(Frequency = length(NonVetService))

ggplot(NonVetService, aes(
  fill = (MostAttach),
  y = Frequency,
  x = NonVetService
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of NonVetService for Dogs and Cats") +
  labs(y = "Frequency of Responces", x = "NonVetService")

ggplot(NonVetService, aes(
  fill = (NonVetService),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of NonVetService  by pet") +
  labs(y = "Freqency of Responces", x = "Since the COVID-19 outbreak, have you made plans for caring for your pet/companion animal(s) should you become sick and unable to care for them?" )

NonVetService.fit = glm(NonVetService ~ MostAttach, family = binomial, data =
                       turk2)
kable(summary(NonVetService.fit)$coef, digits = 2)

```






### NonVetLessFreq : In the past 12 months have you used an animal care service that does NOT normally require a veterinarian?         
```{r turk2NonVetLessFreq, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$NonVetLessFreq  <-
  factor(
    turk2$NonVetLessFreq ,
    levels = c("0", "1"),
    labels = c("No", "Yes")
  )

turk2$MostAttach <-
  factor(
    turk2$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )


tNonVetLessFreq  <- table(turk2$NonVetLessFreq , turk2$MostAttach)
kable(tNonVetLessFreq , caption = "Contingency Table for  NonVetLessFreq ")

NonVetLessFreq  <- turk2 %>%
   dplyr::filter(PetOwner == "Pets=Yes") %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(NonVetLessFreq , MostAttach) %>%
  summarise(Frequency = length(NonVetLessFreq))

ggplot(NonVetLessFreq , aes(
  fill = (MostAttach),
  y = Frequency,
  x = NonVetLessFreq 
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of NonVetLessFreq  for Dogs and Cats") +
  labs(y = "Frequency of Responces", x = "NonVetLessFreq ")

ggplot(NonVetLessFreq , aes(
  fill = (NonVetLessFreq ),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of NonVetLessFreq   by pet") +
  labs(y = "Freqency of Responces", x = "In the past 12 months have you used an animal care service \n that does NOT normally require a veterinarian?" )

NonVetLessFreq.fit = glm(NonVetLessFreq  ~ MostAttach, family = binomial, data =
                       turk2)
kable(summary(NonVetLessFreq.fit)$coef, digits = 2)

```



### WhyNonVetLessFreq : Which of the following best describes why you are using these services less frequently?        
```{r turk2WhyNonVetLessFreq, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")

turk2$NonVetLessFreq  <-
  factor(
    turk2$NonVetLessFreq ,
    levels = c("0", "1"),
    labels = c("No", "Yes")
  )

turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$WhyNonVetLessFreq  <-
  factor(
    turk2$WhyNonVetLessFreq ,
    levels = c("1", "2", "3", "4", "5", "6", "7"),
    labels = c(
    "Concerned about exposure", 
    "Concerned about pets exposure",   
    "Following public health message", 
    "Can't afford now", 
    "Too busy doing other things ", 
    "Services unavailable", 
    "Other" 
)
  )
#summary(turk2$WhyNonVetLessFreq)
turk2$MostAttach <-
  factor(
    turk2$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
summary(turk2$MostAttach)
tWhyNonVetLessFreq <- table(turk2$WhyNonVetLessFreq , turk2$MostAttach)
kable(tWhyNonVetLessFreq, caption = "Contingency Table for WhyNonVetLessFreq ")

WhyNonVetLessFreq  <- turk2 %>%
  dplyr::filter(NonVetLessFreq == "Yes") %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(WhyNonVetLessFreq , MostAttach) %>%
  summarise(Frequency = length(WhyNonVetLessFreq))

ggplot(WhyNonVetLessFreq , aes(
  fill = (MostAttach),
  y = Frequency,
  x = WhyNonVetLessFreq 
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
            coord_flip() +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of WhyNonVetLessFreq  for Dogs and Cats") +
  labs(y = "Frequency of Responces", x = "WhyNonVetLessFreq ")

ggplot(WhyNonVetLessFreq , aes(
  fill = (WhyNonVetLessFreq ),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of WhyNonVetLessFreq   by pet") +
  labs(y = "Freqency of Responces", x = "Which of the following best describes why \n you are using these services less frequently?" )

WhyNonVetLessFreq.fit = glm(WhyNonVetLessFreq ~ MostAttach, family = binomial, data =
                       turk2)
kable(summary(WhyNonVetLessFreq.fit)$coef, digits = 2)

```
### Pet attachement


<div style="margin-bottom:100px;">
### CCAS1: My pet/animal provides me with companionship?       
```{r turk2CCAS1, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$CCAS1 <-
  factor(turk2$CCAS1,
         levels = c("1", "2","3","4","5","6","7"),
         labels = c(
           "Strongly disagree",
           "Disagree" ,
           "Somewhat disagree",
           "Neither agree nor disagree", 
          "Somewhat agree", 
          "Agree", 
          "Strongly agree" 
))


turk2$MostAttach <-
  factor(
    turk2$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk2$MostAttach<-factor(turk2$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tCCAS1 <- table(turk2$CCAS1, turk2$MostAttach)
kable(tCCAS1, caption = "CCAS1: My pet/animal provides me with companionship?")

CCAS1 <- turk2 %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(CCAS1, MostAttach) %>%
  summarise(Frequency = length(CCAS1))

ggplot(CCAS1, aes(
  fill = (MostAttach),
  y = Frequency,
  x = CCAS1
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of CCAS1 by pet") +
  labs(y = "Frequency of Responces", x = "My pet/animal provides me with companionship?")

ggplot(CCAS1, aes(
  fill = (CCAS1),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "My pet/animal provides me with companionship?" )

CCAS1.fit = glm(CCAS1 ~ MostAttach, family = binomial, data =
                       turk2)
kable(summary(CCAS1.fit)$coef, digits = 2)

```


<div style="margin-bottom:100px;">


### CCAS2: Having a pet/animal gives me something to care for?  
```{r turk2CCAS2, echo=F, warning=F} 
library(dplyr)
turk2 <- read_excel("2020-5-6 COVID_Raw_Data.xlsx")
turk2$PetOwner <-
  factor(
    turk2$PetOwner,
    levels = c("0", "1"),
    labels = c("Pets=No", "Pets=Yes")
  )
turk2$CCAS2 <-
  factor(turk2$CCAS2,
         levels = c("1", "2","3","4","5","6","7"),
         labels = c(
           "Strongly disagree",
           "Disagree" ,
           "Somewhat disagree",
           "Neither agree nor disagree", 
          "Somewhat agree", 
          "Agree", 
          "Strongly agree" 
))


turk2$MostAttach <-
  factor(
    turk2$MostAttach,
    levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
    labels = c(
      "Dog",
      "Cat",
      "Horse",
      "Bird",
      "Reptile",
      "Small Mammal" ,
      "Fish",
      "Other"
    )
  )
#turk2$MostAttach<-factor(turk2$MostAttach, levels = c("1","2","3","4","5","6","7","8"), labels = c("Dog", "Cat", "Horse","Other", "Other", "Other" , "Other", "Other"))

tCCAS2 <- table(turk2$CCAS2, turk2$MostAttach)
kable(tCCAS2, caption = "CCAS2: Having a pet/animal gives me something to care for")

CCAS2 <- turk2 %>%
  dplyr::filter(MostAttach == "Dog" | MostAttach == "Cat") %>%
  group_by(CCAS2, MostAttach) %>%
  summarise(Frequency = length(CCAS2))

ggplot(CCAS2, aes(
  fill = (MostAttach),
  y = Frequency,
  x = CCAS2
)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = Frequency),
            position = position_dodge(width = 0.9),
            vjust = -0.25) +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  ggtitle("Frequency distribution of CCAS2 by pet") +
  labs(y = "Frequency of Responces", x = "Having a pet/animal gives me something to care for")

ggplot(CCAS2, aes(
  fill = (CCAS2),
  y = Frequency,
  x = MostAttach
)) +
  geom_bar(position = "fill", stat = "identity") +
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 90
    ),
    axis.text.y = element_text(
      face = "bold",
      color = "#993333",
      size = 10,
      angle = 0
    )
  ) +
  #geom_text(aes(label=Frequency), position=position_dodge(width=0.9), vjust=-0.25)+
  ggtitle("Frequency distribution of ownership time  by pet") +
  labs(y = "Freqency of Responces", x = "Having a pet/animal gives me something to care for?" )

CCAS2.fit = glm(CCAS2 ~ MostAttach, family = binomial, data =
                       turk2)
kable(summary(CCAS2.fit)$coef, digits = 2)

```





